---
title: "Corona Virus Vaccination"
author: "Midhun Thaduru"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    fontsize: 14pt
    highlight: monochrome
    number_sections: no
    theme: cosmo
    toc: yes
  pdf_document:
    toc: yes
---

# Exploratory Data Analysis of Corona Virus Vaccination

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = TRUE, 
                      warning = FALSE, message = FALSE)

# Loading the required libraries
library(data.table)
library(ggplot2)
library(zoo)

# Changing theme of ggplot to black n white
theme_set(theme_bw(12))
```

## Vaccination Dataset

The vaccination dataset is obtained from [Github](https://github.com/owid/covid-19-data). The description along with the dataset is also available on [Kaggle](https://www.kaggle.com/gpreda/covid-world-vaccination-progress).  
```{r vaccination}

VaccinationData <- fread(
  paste0(
    Sys.getenv("Git"), 
    "/CoronaVirus/Datasets/country_vaccinations.csv")
)

VaccinationData[, source_website := NULL]

setorder(VaccinationData, country, date)

```

* It will be assumed that the first day of each country will have 0 `total_vaccinations`, `people_vaccinated`, `people_fully_vaccinated`, `total_vaccinations_per_hundred`, `people_vaccinated_per_hundred`, `people_fully_vaccinated_per_hundred` and `daily_vaccinations_per_million` if the values are NA.  
* It will also be assumed that if the above mentioned columns (except `daily_vaccinations_per_million`) have NAs in-between then there are no vaccinations done on those day and previous values are carried over.  

```{r}

VaccinationData[, c("total_vaccinations",
                    "people_vaccinated",
                    "people_fully_vaccinated",
                    "total_vaccinations_per_hundred",
                    "people_vaccinated_per_hundred",
                    "people_fully_vaccinated_per_hundred",
                    "daily_vaccinations_per_million") := lapply(.SD, 
                                                                function(x){
                                                                  replace(x, seq_along(x) == 1 & is.na(x), 0)
                                                                }), by = "country",
                .SDcols = c("total_vaccinations",
                            "people_vaccinated",
                            "people_fully_vaccinated",
                            "total_vaccinations_per_hundred",
                            "people_vaccinated_per_hundred",
                            "people_fully_vaccinated_per_hundred",
                            "daily_vaccinations_per_million")]

VaccinationData[, c("total_vaccinations",
                    "people_vaccinated",
                    "people_fully_vaccinated",
                    "total_vaccinations_per_hundred",
                    "people_vaccinated_per_hundred",
                    "people_fully_vaccinated_per_hundred") := lapply(.SD, 
                                                                     function(x){
                                                                       na.locf(x, na.rm=FALSE, fromLast=FALSE)
                                                                     }), by = "country",
                .SDcols = c("total_vaccinations",
                            "people_vaccinated",
                            "people_fully_vaccinated",
                            "total_vaccinations_per_hundred",
                            "people_vaccinated_per_hundred",
                            "people_fully_vaccinated_per_hundred")]

```

```{r}

VaccinationData[, vaccines_count := sapply(strsplit(vaccines, ", "), length)]

LatestVaccinationStatus <- VaccinationData[, .SD[.N], by = "country"]

write.csv(LatestVaccinationStatus,
          paste0(Sys.getenv("Git"),
                 "/CoronaVirus/Datasets/latest_vaccination_status.csv"),
          row.names = F)

write.csv(VaccinationData,
          paste0(Sys.getenv("Git"),
                 "/CoronaVirus/Datasets/cleaned_country_vacciation.csv"),
          row.names = F)

```

